{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-11 documents/background.tex
Writing, re-organizing references

@@

\subsection{Liburdy's oxidation-dependent lipid leakage}

\subsection{Tsen femtosecond laser ISRU}

Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
the vibrational mode; the optimal pulse duration is some fraction of the period of the mode in question.
 Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration; 
 unlikely to be of great clinical use.

@@

@@

@@

>>>>

NATO Research Task Group 189 \cite{treatyelectromagnetic}

HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
IEEE C95.1TM-2005 safety standard nor the proposed limit in the Directive 2004/40/EC [33] (subsequently
promulgated as 2013/35/EU [34]) have scientific basis.

The group noted that physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown). Current research efforts by members to expose biological organism(s), tissues, and cells to environmental
fields up to this magnitude have been unable to elicit an acute biological response.

C95.1-2019, B.4.3 Rationale for pulsed RF field limits

Cancer treatment involving irreversible electroporation is in a different regime. Long pulses involving high conduction currents through needles. Cardiac arrest.

H. H. Williams: Furious activity is no substitute for understanding.

@@

\subsection{Liburdy's oxygen-dependent lipid leakage}

\subsection{Tsen's femtosecond laser ISRU}

Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.

Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration of exposure; unlikely to be of great clinical use.

@@

If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.} 
%
, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.

The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.

\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$. Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }

\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon. Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.

	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}

\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}

@@

Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. For instance, data on far UV [Buonanno 2017] indicates safety.\\

@@

To illustrate how sensitive this research is, [Chemeris 2004] mention:

\begin{quote}

	The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C. This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."

\end{quote}

### 2021-01-11 documents/fluorescence.tex
Writing, re-organizing references

%!TeX root = fluroescence
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

@@

The LED was about 3 cm away, and put through a ~3 mm aperture. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.

@@

Performance of this arrangement was very satisfactory. A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts. The

@@

With the setup we’re using and the small quantities, the excitation light is somewhere around ~10^5 times as powerful as the emission. This doesn’t seem to be a big issue gel-docs, picking out bands on gels - they don’t usually seem to use excitation filters; however, to get the excitation bleed-through low enough to do this quantitative assay, the bleed-through must be really low, and in our testing proper dielectric filters are required on both the excitation and emission sides.

@@

Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting.

No shutters or anything required.

@@

Gel-docs , with spectra specified using the Wratten scale. These do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.

Epiflurorescence means the Most commercial microscopes use dichroic beamsplitters, allowing the excitation beam beam to go through the same objective. The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive. With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was unnecessary.

@@

Gating the photomultiplier HV is another technique.

@@

Silicon photomultipliers like ON's C−Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.

>>>>

%!TeX root = fluorescence
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{fluro_1}
	\caption{}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{fluro_2}
	\caption{}
\end{figure}

For one thing, GelGreen appears to be eminiently stable - samples can be stored for long periods of time; pre-mixed batches.

\subsection{Light source}

A modulation frequency of

Lexan fluro was unex

Acridine orange (N-alkylacridinium)

Orange 16

@@

the microscope is largely unnecessary.

@@

The LED was about 3 cm away, and put through a ~3 mm aperture in a piece of PVC pipe. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.

@@

Performance of this arrangement was very satisfactory. A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately $\pm 1500$ counts. The

@@

With the setup we’re using and the small quantities, the excitation light is somewhere around ~$10^5$ times as powerful as the emission. This doesn’t seem to be a big issue gel-docs, picking out bands on gels - they don’t usually seem to use excitation filters; however, to get the excitation bleed-through low enough to do this quantitative assay, the bleed-through must be really low, and in our testing proper dielectric filters are required on both the excitation and emission sides.

@@

Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting; no shutters or anything required. Gating the photomultiplier HV is another technique.

@@

Gel-docs , with spectra specified using the Wratten scale. These filters alone do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.

Most commercial microscopes use dichroic beamsplitters, allowing the excitation and emission beam to go through the same objective. The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive. With fiber optic excitation at right angles to the objective, excitation scattering was low enough that the dichroic was unnecessary.

@@

@@

Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.

### 2021-01-11 documents/molecular_dynamics.tex
Writing, re-organizing references

Liposome wrapped with BUMPy\cite{BUMPy2018}. \footnote{Durrant's LipidWrapper are equally good options}. MARTINI 
coarse-grained 
lipid and water force field. Run with GROMACS (5?) on the GPU.\footnote{\it "H. H. Williams: Furious activity is no substitute 
	for understanding.".}  A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (? N/m spring constant) and a strong thermostat () to crudely emulate a large thermal bath (an "open boundary"). This may not be a good way to do this.

@@

Rather than use built-in normal-mode methods, Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a 
really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.

Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or some other, more repeatable "pipeline manager" should have been used}. Elec

Coarse-grained models of COVID with mechanically have recently

>>>>

Liposome wrapped with BUMPy\cite{BUMPy2018}. \footnote{Durrant's LipidWrapper are equally good options}. MARTINI 
coarse-grained 
lipid and water force field. Run with GROMACS (5?) on the GPU. A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (? N/m spring constant) and a strong thermostat () to crudely emulate a large thermal bath (an "open boundary"). This may not be a good way to do this.

@@

Rather than use standard eigenmode-style normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.

Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or RENKU or some other, more repeatable and reproducible "pipeline manager" should have been used}.

Polarizable water is usually required

Coarse-grained models of COVID with mechanically have recently been created; as of this writing the all-important nucleocapsid and RNA
